Why ordered beta regression

### 2023-09-15 notebook/ordbeta.qmd
tiny typos

The distribution of our outcome here—the number of provinces an INGO is authorized to work in—posts a unique statistical challenge. It's a mix of three different processes. 30ish% of INGOs are registered only in one province, 40% are registered in all provinces, and the remaining 30ish% are registered in 2–31 provinces.

@@

```{r plot-province-prop}
ongo |> 
  mutate(province_prop = provinces_to_prop(province_count)) |> 
  # Add some variables for plotting
  mutate(
    is_zero = province_prop == 0,
    is_one = province_prop == 1,
    province_prop = case_when(
      is_zero ~ -0.01,
      is_one ~ 1.02,
      .default = province_prop
    )
  ) |> 
  mutate(outcome_type = case_when(
    is_zero ~ "1 province (0%)",
    is_one ~ "32 provinces (100%)",
    .default = "2–32 provinces"
  )) |> 
  ggplot(aes(x = province_prop)) +
  geom_histogram(
    aes(fill = outcome_type),
    bins = 32, linewidth = 0.1, boundary = 0,
    color = "white") +
  scale_x_continuous(labels = label_percent()) +
  scale_y_continuous(breaks = seq(0, 250, 50)) +
  scale_fill_manual(values = clrs[c(3, 5, 7)]) +
  labs(
    x = "Scaled proportion of provinces INGOs are authorized to work in", 
    y = "Count", fill = NULL) +
  theme_ongo()
```

>>>>

The distribution of our outcome here—the number of provinces an INGO is authorized to work in—poses a unique statistical challenge. It's a mix of three different processes. 30ish% of INGOs are registered only in one province, 40% are registered in all provinces, and the remaining 30ish% are registered in 2–31 provinces.

@@

```{r plot-province-prop}
ongo |> 
  mutate(province_prop = provinces_to_prop(province_count)) |> 
  # Add some variables for plotting
  mutate(
    is_zero = province_prop == 0,
    is_one = province_prop == 1,
    province_prop = case_when(
      is_zero ~ -0.01,
      is_one ~ 1.02,
      .default = province_prop
    )
  ) |> 
  mutate(outcome_type = case_when(
    is_zero ~ "1 province (0%)",
    is_one ~ "32 provinces (100%)",
    .default = "2–31 provinces"
  )) |> 
  ggplot(aes(x = province_prop)) +
  geom_histogram(
    aes(fill = outcome_type),
    bins = 32, linewidth = 0.1, boundary = 0,
    color = "white") +
  scale_x_continuous(labels = label_percent()) +
  scale_y_continuous(breaks = seq(0, 250, 50)) +
  scale_fill_manual(values = clrs[c(3, 5, 7)]) +
  labs(
    x = "Scaled proportion of provinces INGOs are authorized to work in", 
    y = "Count", fill = NULL) +
  theme_ongo()
```
